### 2024-02-23 ms.qmd
Update ms.qmd

Behavioural flexibility, i.e. the ability to adjust the behaviour adaptively in response to internal or external changes by problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can]. In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can]. For instance, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural]. According to the adaptive flexibility hypothesis, behavioural flexibility is particularly relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that can involve more than one generation. If behavioural flexibility is adaptive in these different phases, both this trait and the underlining mechanisms are expected to persist through generations in successful invaders. For example, in mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011]. Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success. As such, we find that studying the effect of developmental conditions on behavioural flexibility can be key to understand and predict the success of invasive species.  
**BETTER LINK**In this scenario, prenatal glucocorticoids (GCs) and thermal environment can be salient factors in the study of behavioural flexibility within the context of invasion biology. GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023]. In addition, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic]. For instance, young Sprague-Dawley rats treated with corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while cold incubation temperatures in the eastern three-lined skink resulted in significant impairments with behavioural flexibility [@clark_colour_2014]. Moreover, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].  
Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L. delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI]. Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L. delicata_, and are likely key for its invasive success [@chapple_know_2011; @chapple2012can; @bezzina2014does]. However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remains unknown. To investigate these effects, we first manipulated CORT levels and incubation temperature in eggs from both species, and then subjected the juveniles to a reversal learning task as a measure of behavioural flexibility [@brown2010behavioral; @szabo2020can]. We predicted that _L. delicata_ would, on average, perform more proficiently in the task that _L. guichenoti_. We also predicted that prenatal CORT and temperature would affect the behavioural flexibility of both species, but that _L. guichenoti_ would be more impacted by the prenatal treatments than _L. delicata_. High prenatal temperatures are considered to improve performance in cognitive tasks in some ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]. For this reason, we predicted that lizards incubated at higher temperatures would perform better in the learning reversal task. Conversely, we predicted that prenatal CORT would impair learning [as seen previously in @lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic]. Finally, we expected an interaction between both treatments, with high temperatures mitigating the negative effects of prenatal CORT on the performance of the lizards in the task. This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures accelerates the metabolism of CORT, resulting in embryos being exposed to CORT for a shorter time.

@@

#### Experimental design
For this study, we used juveniles of _L. delicata_ and _L. guichenoti_ that came from a breeding colony kept in the lab. This colony, established in 2019, originates from animals collected in Sydney, likely from similar populations that have become invasive on Lord Howe Island [@chapple2016origin] (details of breeding colony and husbandry in Supplementary Material). To see the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol ('CORT' treatment) or the same volume of the vehicle ('Control'), and were then incubated at different temperatures ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) until hatching.  
To estimate behavioural flexibility, we examined lizards' performance in a reversal learning task using colour as the main conditioned stimulus and food (frozen small *A. domestica*) as a reward (see @fig-Methods). The learning test was divided in three main phases: (1) _habituation_ -  lizards were conditioned to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); (2) _association_ - lizards were conditioned to associate food with one colour (Fig. 1 Associative task); and (3) _reversal_ - the colour associated with the food was changed (Fig. 1 Reversal task). For the associative and reversal phases we used three different ramps that were identical in size and shape to the ones for the habituation phase. The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. To control for potential colour biases, we assigned one group of lizards to associate the blue ramp with the accessible food in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. To avoid the use of chemical cues, we placed the food reward in all three ramps, but in two of them the cricket was covered by small white lids with holes on the top. Lizards were tested once daily between 11 to 12 am, when lizards are active. The habituation phase lasted 38 days, the association phase 35, and the reversal phase 40 days. We recorded and analysed manually all trials form the association and reversal phases using a standard video player (IINA). Videos were analysed by one person (P.R.) who was blind to the treatment groups. We used as the main variable whether the animal chose the correct ramp first or not. We considered that a choice was made if the head of the lizard was inside the well of one of the ramps. Lizards were considered to make a correct choice if they chose the ramp with the accessible food first. We scored lizards that chose ramps with inaccessible foods first to have made an incorrect choice. We considered a trial failed if there was no choice in one hour of recording and those trials were considered as ‘non data’ in the analyses. Here, we analysed the data of the reversal as an index of behavioural flexibility [@brown2010behavioral].

@@

We performed the analyses for both species separately. We fitted a total of two different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022). We had per each model four parallel chains of 3000 iterations, with a warmup interval of 1000 iterations. We used 'Choice' - whether the individual chose correct (1) or not (0) - as the response variable; and trial, hormone ('CORT' versus 'Control'), incubation temperature ('Cold' versus 'Hot'), and their interaction as fixed factors. Lizard identity was employed as a random intercept, and as a random slope we included the trial within each level of lizard identity. We used the posterior distributions of these models to evaluate differences in learning rate between treatments and species. Learning slopes were obtained using the estimates of the variable trial per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not. We used the pmcmc method to test whether those slopes or the comparisons between treatments (e.g. slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) or species were different from zero (two-tailed tests). We considered statistical significance if p-value < 0.05.

@@

#| tbl-cap: "Estimates of Reversal learning slope for all the different treatments per each task, species, and group. Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero. In bold, those values that are significant (p-value <0.05)"

@@

We found that the learning slopes for all treatments and species were higher from zero, but we did not find any difference between treatments or species. There were not significant differences between treatments in _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_dec(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_dec(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results). When pooled together, we did not find any significant effect of incubation temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`). Finally, there were not significant differences when we compared the estimated slopes between species (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).

@@

The study embarked on unravelling the interactive effects of prenatal temperature and Glucocorticoids (GCs) on behavioral flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). Despite sharing life history traits, only _L. delicata_ has proven successful in colonizing various global regions, and we hypothesized this may be related with higher behavioural flexibility. Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion that can involve more than one generation. Nevertheless, we did not find any significant differences between treatments or species when we compared their performance in a reversal task. We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate. Furthermore, these results were consistent when only those individuals that performed better in the previous associative task were included (see Supplementary material).  
Previous studies have shown that _L. delicata_ more readily explores novel environments than _L. guichenoti_, which can be advantageous during colonization [@chapple_know_2011]. However, Bezzina et al. [@bezzina2014does] found no differences in learning between the two skinks in an associative learning task. Our results align with the latter study and suggest that behavioural flexibility does not differ between these species. In addition, we did not find any effect of the treatments on both species. Both results contrast our original predictions and may indicate that other aspects of their biology are more relevant for _L. delicata_ success as invaders than behavioural flexibility. For instance, the mentioned differences in exploratory behaviour can be the key factor explaining why _L. delicata_ and not _L. guichenoti_ is better at colonising new areas, since exploring more can also enhance the ability to effectively locate novel resources in _L. delicata_ [@chapple_know_2011].  
Our early environment manipulation did not affect the performance of the lizards in the task. We predicted that prenatal CORT treatment would decrease reversal learning abilities and that high temperatures would minimize these effects. However, our results show no significant differences between treatments in both species. Our outcome contrast with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], but they are consistent with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016]. More striking is the absence of effect of incubation temperature, since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]. Furthermore, those studies that reported cold-incubated lizards learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in the hot treatment. In some systems, exposure to CORT during development has hermetic effects on  learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012]. For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced density of immature neurons and cell proliferation and in the dentate gyrus [@DOSEneurobrummelte2010chronic]. We know that prenatal CORT treatment affects  other traits in both species of lizards used in this experiment (unpublished data). However, it is possible that prenatal CORT treatment affects tissues differently. Conversely, we find more plausible that the effects of the early environment may vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000]. These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks, and by measuring the neurophysiological effects on different brain nuclei.  
In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioral flexibility, at similar rates, with no discernible differences between treatments or species. These findings contrast our initial predictions and suggest that other aspects of _L. delicata_ biology may be more influential for their success as invaders than behavioral flexibility alone. The present study also indicates that prenatal CORT and temperature do not affect learning abilities in these species. Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks, as well as the effects of both treatments on brain function.

>>>>

Behavioural flexibility describes the ability to adjust behaviour adaptively in response to internal or external changes by problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can]. Generally, species with higher behavioural flexibility are more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can]. For instance, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural]. According to the adaptive flexibility hypothesis, behavioural flexibility is most relevant during introduction, establishment, and spreading stages of the population into new habitats [@wright2010behavioral; @chapple2012can; @szabo2020can]. These stages can involve more than one generation, so selection may act on behavioural flexibility and the underlying mechanisms in successful invaders to ensure the persistence of behavioural flexibility through generations. In mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011]. Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of future generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success. As such, we find that studying the effect of developmental conditions on behavioural flexibility can be key to understanding and predicting invasive species' success.  
**BETTER LINK**In this scenario, prenatal glucocorticoids (GCs) and the thermal environment can be salient factors in the study of behavioural flexibility within invasion biology. GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023]. In addition, there is evidence that developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic]. For instance, young Sprague-Dawley rats treated with corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while cold incubation temperatures in the eastern three-lined skink resulted in significant impairments with associative and reversal learning [@clark_colour_2014]. Moreover, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].  
Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L. delicata_ has successfully colonised different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI]. Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L. delicata_, and are likely key to its invasive success [@chapple_know_2011; @chapple2012can; @bezzina2014does]. However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remain unknown. To investigate these effects, we first manipulated CORT levels and incubation temperature in eggs from both species, then subjected the juveniles to a reversal learning task to measure behavioural flexibility [@brown2010behavioral; @szabo2020can]. We predicted that _L. delicata_ would, on average, perform more proficiently in the task than _L. guichenoti_. We also predicted that prenatal CORT and temperature would affect the behavioural flexibility of both species and that _L. guichenoti_ would be more impacted by the prenatal treatments than _L. delicata_. **The rationale behind this prediction is that behavioural flexibility is expected to be preserved through generations in invassive species, and as such, less impacted by early environment.** Further, we predicted those incubated at higher temperatures to perform better in the reversal task because high prenatal temperatures often improve performance in cognitive tasks in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]. Conversely, we predicted that prenatal CORT would impair learning as shown in other species [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic]. Finally, we expected an interaction between both treatments, with high temperatures mitigating the negative effects of prenatal CORT on the performance of the lizards in the task. This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures accelerates the metabolism of CORT, resulting in embryos being exposed to CORT for a shorter time.

@@

#### Experimental design
For this study, we used juveniles of _L. delicata_ and _L. guichenoti_ from a breeding colony kept in the lab. Established in 2019, this colony originates from animals collected in Sydney, likely from similar populations that have become invasive on Lord Howe Island [@chapple2016origin] (details of breeding colony and husbandry in Supplementary Material). To test the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (CORT treatment) or the same volume of the vehicle (Control), and were then incubated at different temperatures (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) until hatching.  
To estimate behavioural flexibility, we examined lizards' performance in a reversal learning task using colour as the primary conditioned stimulus and food (frozen small *A. domestica*) as a reward (see @fig-Methods). The learning test was divided into three main phases: (1) _habituation_ -  lizards were conditioned to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); (2) _association_ - lizards were conditioned to associate food with one colour (Fig. 1 Associative task); and (3) _reversal_ - the colour associated with the food was changed (Fig. 1 Reversal task). For the associative and reversal phases we used three different ramps that were identical in size and shape to the ones for the habituation phase. The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. To control for potential colour biases, we assigned one group of lizards to associate the blue ramp with the accessible food in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. To avoid the influence of chemical cues, we placed the food reward in the wells of all three ramps, but in two of the wells the cricket was covered by immovable small white lids with holes on the top. Lizards were tested once daily between 11 to 12 am, when lizards are active. The habituation phase lasted 38 days, the association phase 35, and the reversal phase 40 days. We recorded and analysed manually all trials form the association and reversal phases using a standard video player (IINA). Videos were analysed by one person (P.R.) who was blind to the treatment groups. We used as the main variable whether the animal chose the correct ramp first or not. We considered that a choice was made if the head of the lizard was inside the well of one of the ramps. Lizards were considered to make a correct choice if they chose the ramp with the accessible food first. We scored lizards that chose ramps with inaccessible foods first to have made an incorrect choice. We considered a trial failed if there was no choice in one hour of recording and those trials were considered as ‘non data’ in the analyses. Here, we analysed the data of the reversal as an index of behavioural flexibility [@brown2010behavioral].

@@

We performed the analyses for each species separately. We fitted a total of two different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022). We had per each model four parallel chains of 3000 iterations, with a warm-up interval of 1000 iterations. We used Choice - whether the individual chose correct (1) or not (0) - as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and their interaction as fixed factors. Lizard identity was employed as a random intercept, and as a random slope, we included the trial within each level of lizard identity. We used the posterior distributions of these models to evaluate differences in learning rate between treatments and species. Learning slopes were obtained using the estimates of the variable trial per each level of the hormone-temperature interaction (Treatments); values greater than zero were considered as evidence of learning, while those less or equal to zero were not. We used the pmcmc method to test whether those slopes or the comparisons between treatments (e.g. slope for CORT-Cold lizards minus CORT-Hot lizards) or species differed from zero (two-tailed tests). We considered statistical significance if p-value < 0.05.

@@

#| tbl-cap: "Estimates of Reversal learning slope for all the different treatments per each task, species, and group. Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and tested the hypothesis that the mean equals zero. In bold, those values that are significant (p-value <0.05)"

@@

**Change RESULTS????** We found that the learning slopes for all treatments and species were higher from zero, but we did not find any difference between treatments or species. There were not significant differences between treatments in _L. delicata_ (Control-Cold - CORT-Cold = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_dec(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_dec(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L. guichenoti_ (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results). When pooled together, we did not find any significant effect of incubation temperature (_L. delicata_: Hot learning slope - Cold learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L. guichenoti_: Hot learning slope - Cold learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) or the hormone (_L. delicata_: Control learning slope - CORT learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L. guichenoti_: Control learning slope - CORT learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`). Finally, there were not significant differences when we compared the estimated slopes between species (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).

@@

The study embarked on unravelling the interactive effects of prenatal temperature and GCs on behavioural flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). Despite sharing life history traits, only _L. delicata_ has proven successful in colonising various global regions, and we hypothesised this may be related to higher behavioural flexibility. Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion involving more than one generation. Nevertheless, we did not find significant differences between treatments or species when we compared their performance in a reversal task. We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate. Furthermore, these results were consistent when only those individuals that performed better in the previous associative task were included (see Supplementary material).  
Previous studies have shown that _L. delicata_ more readily explores novel environments than _L. guichenoti_, which can be advantageous during colonisation [@chapple_know_2011]. However, Bezzina et al. [@bezzina2014does] found no differences in learning between the two skinks in an associative learning task. Our results align with the latter study and suggest that behavioural flexibility does not differ between these species. In addition, we did not find any effect of the treatments on either species. Both results contrast our original predictions and may indicate that other aspects of their biology are more relevant for _L. delicata_'s success as invaders than behavioural flexibility. For instance, the mentioned differences in exploratory behaviour can be the key factor explaining why _L. delicata_ and not _L. guichenoti_ is better at colonising new areas, since exploring more can also enhance the ability to effectively locate novel resources in _L. delicata_ [@chapple_know_2011].  
Our early environment manipulation did not affect the lizards' performance in the task. We predicted that prenatal CORT treatment would decrease reversal learning abilities and that high temperatures would minimise these effects. However, our results show no significant differences between treatments in both species. Our outcome contrasts with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], but they are consistent with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016]. More striking is the absence of an effect of incubation temperature since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]. Furthermore, those studies that reported cold-incubated lizards learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in the hot treatment. In some systems, exposure to CORT during development has hormetic effects on  learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012]. For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced density of immature neurons and cell proliferation and in the dentate gyrus [@DOSEneurobrummelte2010chronic]. We know that prenatal CORT treatment affects other traits in both species of lizards used in this experiment (unpublished data). However, it is possible that prenatal CORT treatment affects tissues differently. Conversely, it is likely that the effects of the early environment may vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000]. These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks, and by measuring the neurophysiological effects on different brain nuclei.  
In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioural flexibility, at similar rates, with no discernible differences between treatments or species. These findings contrast our initial predictions and suggest that other aspects of _L. delicata_ biology may be more influential for their success as invaders than behavioural flexibility alone. The present study also indicates that prenatal CORT and temperature do not affect learning abilities in these species. Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks and the effects of both treatments on brain function.
